**Density Dependence**

### 2023-02-09 Rmd/runDD.Rmd

```{r}
source("../R/dd.R")
```

```{r, dbox}
dropboxdir<-try(file.path(get_dropbox(), "dd"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"
```

@@

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel("../data/inputs/dat.xlsx",3))
```

```{r eq}
par=teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Scomber scombrus"]
par=lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
eq =lhEql(par,m="lorenzen")

@@

```{r}
save(eq,file="~/Desktop/eq.RData")
```

@@

```{r}
save(eq,file="/home/laurie/Desktop/tmp/t.RData")
```

@@

```{r}
save(eq,parMat,par,sr,file="/home/laurie/Desktop/tmp/t.RData")
```

```{r}
load("/home/laurie/Desktop/tmp/t.RData")

>>>>

```{r}
source("../R/dd.R")
source("../R/get_dropbox.R")

dropboxdir<-try(file.path(get_dropbox(), "pelagics"))

if ("try-error"%in%is(dropboxdir))
  dropboxdir="~/Dropbox/pelagics"

load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel("../data/inputs/dat.xlsx",3))

```

@@

```{r eq}
par=FLife::teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Scomber scombrus"]
par=FLife::lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
eq =FLife::lhEql(par,m="lorenzen")

@@

```{r}
# save(eq,file="~/Desktop/eq.RData")
```

@@

```{r}
# save(eq,file="/home/laurie/Desktop/tmp/t.RData")
```

@@

```{r}
# save(eq,parMat,par,sr,file="/home/laurie/Desktop/tmp/t.RData")
```

```{r}
# load("/home/laurie/Desktop/tmp/t.RData")
